NURM: a tool to locate numerical differences in pipelines

### 2019-10-09 paper.tex
A few fixes in results

We identified four types of subjects with different PreFreeSurfer process
trees (Table~\ref{table:data-clusters}). Differences between subject types
are coming from different  numbers of T1 and T2 images in the raw data:
subjects of type 1 have 2 T1 images and 2 T2 images, while subjects of type
2 only have 1 T1 image and 1 T2 image. This leads to
different sets of output files. We verified that the process trees were
identical for all subjects of the same type in different versions of
CentOS.

@@

Figure~\ref{fig:pfs_freq} shows the frequency of the processes that create differences 
in the pipeline (the number in the bracket).
Furthermore, this figure represents the percentage of the processes that introduce 
differences along with the sub-pipelines, including linear registration 
with “\emph{FLIRT}” (in ACPC-Alignment, Brain Extraction, Distortion Correction, 
Atlas Registration), non-linear registration with “\emph{FNIRT}” (in Brain Extraction 
and Altas Registration), image warping with “\emph{new\_invwarp}” (in Brain Extraction 
and Atlas Registration). 
Besides, differences were observed in image mean and standard-deviation 
computations in image interpolation with “\emph{fslmaths}” (in Anatomical Average).

>>>>

We identified four types of subjects with different PreFreeSurfer process
trees (Table~\ref{table:data-clusters}). Differences between subject types
are coming from different  numbers of T1 and T2 images in the raw data:
subjects of type 1 have 2 T1 images and 2 T2 images, while subjects of type
2 only have 1 T1 image and 1 T2 image. This leads to
different sets of output files. We verified that the process trees were
identical for all subjects of the same type, for both versions of
CentOS.

@@

Figure~\ref{fig:pfs_freq} shows the frequency at which  processes create differences 
in the pipeline, and how differences are distribute among sub-pipelines.
Differences were observed in linear registration 
with FSL FLIRT (in ACPC-Alignment, Brain Extraction, Distortion Correction, 
Atlas Registration), in non-linear registration with FSL FNIRT (in Brain Extraction 
and Altas Registration), and in image warping with FSL \emph{new\_invwarp} (in Brain Extraction 
and Atlas Registration). 
Differences were also observed in image mean 
computations with FSL maths  (in Anatomical Average).
